From Reversible Programs to \\ Univalent Universes and Back

### 2021-06-10 Pi+/paper/finite.tex
Add sketch of Fin-Lehmer proof

\begin{proposition}
  For all $n:\Nat$,
  \[
    \Lehmer[n] \eqv \Aut[\Fin[n]]
  \]
\end{proposition}

\begin{proof}
  We have to turn this algorithm into a constructive proof in type theory where
  we only use functions and recursion. \todo{Describe the agda code.}
\end{proof}

>>>>

We define a type family $\FinExcept{n} : \Fin[n] \to \UU$ which picks out all elements in $\Fin[n]$ except the one
provided. Note that $\FinExcept{n}[i]$ for $i : \Fin[n]$ is a subtype of $\Fin[n]$ and is hence an $\hSet$.

\begin{definition}
  \( \FinExcept{n}[i] \defeq \dsum{j : \Fin[n]}{i \neq j} \).
\end{definition}

\begin{proposition}
  For any $k : \Fin[n]$, $\unit \sqcup \FinExcept{n}[k] \eqv \Fin[n]$.
\end{proposition}

\begin{proposition}
  For any $k : \Fin[\suc[n]]$, $\FinExcept{\suc[n]}[k] \eqv \Fin[n]$.
\end{proposition}

\begin{proposition}
  For any $n : \Nat$,
  \( \Aut[\Fin[\suc[n]]] \eqv \dsum{k : \Fin[\suc[n]]}{\FinExcept{\suc[n]}[\fzero] \eqv \FinExcept{\suc[n]}{k}} \).
\end{proposition}

\begin{proposition}
  For all $n:\Nat$, \( \Lehmer[n] \eqv \Aut[\Fin[n]] \).
\end{proposition}

\begin{proof}
  For $n = 0$, note that $\Lehmer[0]$ is contractible, and so is $\Aut[\Fin[0]]$. For $n = \suc[m]$, we have the
  following chain of equivalences.
  \[\arraycolsep=0.5em\def\arraystretch{1.5}
    \begin{array}{rl}
      & \Aut[\Fin[\suc[m]]] \\
      \eqv & \dsum{k : \Fin[\suc[m]]}{\FinExcept{\suc[m]}[\fzero] \eqv \FinExcept{\suc[m]}[k]} \\
      \eqv & \dsum{k : \Fin[\suc[m]]}{\FinExcept{\suc[m]}[\fzero] \eqv \Fin[m]} \\
      \eqv & \dsum{k : \Fin[\suc[m]]}{\Fin[m] \eqv \Fin[m]} \\
      \eqv & \Fin[\suc[m]] \times \Aut[\Fin[m]] \\
      \eqv & \Fin[\suc[m]] \times \Lehmer[m] \\
    \end{array}
  \]
\end{proof}
